Estimating Life-Stage Specific Habitat Capacity for Anadromous Salmonids using Quantile Random Forest Models

### 2020-01-31 analysis/paper/paper.Rmd
added some river lines to the watershed map plot

@@

```{r wtsd-map, fig.cap = "Watersheds with CHaMP habitat data. Watersheds in black also contain paired fish data. Watershed names are: 1 - Entiat, 2 - John Day, 3 - Lemhi, 4 - Methow, 5 - Minam, 6 - Secesh, 7 - South Fork Salmon, 8 - Tucannon, 9 - Upper Grande Ronde, 10 - Wenatchee, 11 - Yankee Fork."}
ggplot(data = champ_wtsds) +
  geom_sf() +
  geom_sf(data = champ_wtsds %>%
            filter(fish_data),
          fill = 'black') +
  geom_sf_label(aes(label = id),
                position = position_dodge(width = 200)) +
                # position = position_nudge(x = 5000,
                #                           y = -5000)) +
  theme(axis.title = element_blank())
```

>>>>

<!-- A test commit and push from Sarah's machine -->
<!-- need to do one more test -->

@@

```{r wtsd-map, fig.cap = "Watersheds with CHaMP habitat data. Watersheds in black also contain paired fish data. Watershed names are: 1 - Entiat, 2 - John Day, 3 - Lemhi, 4 - Methow, 5 - Minam, 6 - Secesh, 7 - South Fork Salmon, 8 - Tucannon, 9 - Upper Grande Ronde, 10 - Wenatchee, 11 - Yankee Fork."}
river_lines = QRFcapacity::get_flowlines(stream_order = 6,
                                         champ_wtsds %>%
                                           st_union() %>%
                                           st_make_grid(n = 1)) %>%
            filter(!grepl('^1701', reachcode),
                   !grepl('^171', reachcode))

# river_lines %>%
#   filter(!gnis_name %in% c('Deschutes River',
#                            'Crooked River',
#                            'Payette River',
#                            'North Fork Payette River')) %>%
#   ggplot() +
#   geom_sf(aes(color = gnis_name))

ggplot(data = champ_wtsds) +
  geom_sf(data = river_lines %>%
            filter(!gnis_name %in% c('Deschutes River',
                                     'Crooked River',
                                     'Payette River',
                                     'North Fork Payette River')),
          color = 'darkblue') +
  geom_sf() +
  geom_sf(data = champ_wtsds %>%
            filter(fish_data),
          fill = 'black') +
  geom_sf_label(aes(label = id),
                position = position_dodge(width = 200)) +
  theme(axis.title = element_blank())
